Hydras \& Co.

### 2023-04-28 doc/chapter-fol.tex
Examples of new notations (doc / MoreAck)

If we define a few new notations, the notation scope \texttt{fol\_scope} allow us to parse and print formulas in a less clumsy way.

@@

@@

\inputsnippets{FolExamples/toyNotationForm2}
\begin{remark}[bound variables]
\inputsnippets{FolExamples/boundVars}  
\end{remark}

>>>>

In order to make the first order formulas more readable, we use a generic notation scope called \texttt{fol\_scope}, which uses mainly \coq's 
notations for connectives and quantifiers. The \texttt{\%fol} delimiter 
allows the user to distinguisf \texttt{FOL} connectives from their \coq equivalent.

@@

In addition to \texttt{fol\_scope}, we introduce a few abbreviations specific to our toy language.

@@

The following interactions show how the formulas on $L$ may be 
parsed or printed.

\inputsnippets{FolExamples/toyNotationForm2}

\begin{remark}[bound variables]
\inputsnippets{FolExamples/boundVars}  
\end{remark}
